IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model

### 2021-04-29 main.tex
:triangular_flag_on_post: arXiv and TCom 290421

\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{array}
% \usepackage{caption}
\usepackage{cite}
\usepackage{colortbl}
\usepackage{environ}
\usepackage{grffile}
\usepackage{hyperref}
\usepackage{import}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{siunitx}
\usepackage{stfloats}
\usepackage{tikz}
\usepackage{url}
\usepackage{xcolor}
\usepackage[RPvoltages]{circuitikz}
\usepackage[T1]{fontenc}
\usepackage[caption=false,font=footnotesize]{subfig}
% \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
% \usepackage[cmintegrals]{newtxmath}
\usepackage[short]{optidef}

@@

			\emph{Notations:} Scalars, vectors and matrices are denoted respectively by italic, bold lower-case, and bold upper-case letters. $j$ denotes the imaginary unit. $\boldsymbol{0}$ and $\boldsymbol{1}$ denote respectively zero and one vector or matrix. $\boldsymbol{I}$ denotes the identity matrix. $\mathbb{R}^{x \times y}$ and $\mathbb{C}^{x \times y}$ denote respectively the subspace spanned by real and complex $x \times y$ matrices. $\Re\{\cdot\}$ and $\Im\{\cdot\}$ denote respectively the real and imaginary part of a complex entity. $(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $(\cdot)^+$, $\lvert{\cdot}\rvert$, $\lVert{\cdot}\rVert$ represent respectively the conjugate, transpose, conjugate transpose, ramp function, absolute value, and Euclidean norm. $\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{tr}(\cdot)$, $\mathrm{diag}(\cdot)$ and $\mathrm{diag}^{-1}(\cdot)$ denote respectively the argument, rank, trace, a square matrix with input vector on the main diagonal, and a vector retrieving the main diagonal of the input matrix. $\boldsymbol{S} \succeq \boldsymbol{0}$ means $\boldsymbol{S}$ is positive semi-definite. $\mathbb{A}\{\cdot\}$ extracts the DC component of a signal. $\mathbb{E}_X\{\cdot\}$ takes expectation w.r.t. random variable $X$ ($X$ is omitted for simplicity). The distribution of a CSCG random vector with mean $\boldsymbol{0}$ and covariance $\boldsymbol{\Sigma}$ is denoted by $\mathcal{CN}(\boldsymbol{0},\boldsymbol{\Sigma})$. $\sim$ means ``distributed as''. $(\cdot)^{(i)}$ and $(\cdot)^{\star}$ denote respectively the $i$-th iterate and the stationary solution.
		\end{subsection}
	\end{section}

@@

			Note that $t_{\mathrm{I/P},0}=\mathrm{tr}(\boldsymbol{C}_{\mathrm{I/P},0}\boldsymbol{\Phi})$ is real because $\boldsymbol{C}_{\mathrm{I/P},0}$ and $\boldsymbol{\Phi}$ are Hermitian matrices. Due to symmetry \cite{Huang2017}, we have

			\begin{equation}\label{eq:coupled_terms}
				\sum_{k=-N+1}^{N-1} \Re\left\{t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^*\right\} = \sum_{k=-N+1}^{N-1} t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^*.
			\end{equation}

@@

	\begin{section}{Performance Evaluations}\label{se:performance_evaluation}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{0.9\columnwidth}
			\import{assets/}{layout.pdf_tex}
			\caption{System layout in simulation.}
			\label{fi:layout}
		\end{figure}
		To evaluate the performance of the proposed IRS-aided SWIPT system, we consider the layout in Fig.~\ref{fi:layout} where the IRS moves along a line parallel to the AP-UE path. Let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the AP to the IRS, and denote respectively $d_{\mathrm{D}}$, $d_{\mathrm{I}}=\sqrt{d_{\mathrm{H}}^2+d_{\mathrm{V}}^2}$, $d_{\mathrm{R}}=\sqrt{(d_{\mathrm{D}}-d_{\mathrm{H}})^2+d_{\mathrm{V}}^2}$ as the distance of direct, incident and reflective links. Consider a large open space Wi-Fi-like environment at center frequency \SI{5.18}{\GHz}, where the fading parameters follow IEEE TGn channel model D \cite{Erceg2004} and the reference path loss is \SI{-35}{\dB} at \SI{1}{\meter}. Denote $\Lambda_{\mathrm{D}},\Lambda_{\mathrm{I}},\Lambda_{\mathrm{R}}$ as the path loss of direct, incident and reflective links. All channels are assumed NLoS with taps modelled as i.i.d. CSCG random variables of unit average sum-power, corresponding to a normalized multipath response. Rectenna parameters are chosen as $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\SI{50}{\ohm}$ such that $\beta_2=0.17$ and $\beta_4=957.25$. The average Effective Isotropic Radiated Power (EIRP) is fixed to $P=\SI{36}{\dBm}$ and the receive antenna gain is \SI{2}{\dBi}. For the algorithms, the scaling ratio is $\alpha=2$, the tolerance is $\epsilon=10^{-8}$, and we assume $\delta=\rho$ for simplicity. Each R-E region is averaged over \num{300} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.

@@

			We then derive the gradient explicitly and rewrite \eqref{eq:gradient} as
			\begin{equation}
				\boldsymbol{\Upsilon}^\star = \boldsymbol{I} - \boldsymbol{\Delta}^\star
			\end{equation}
			where $\boldsymbol{\Delta}^\star$ is defied in \eqref{eq:delta}.
			\begin{figure*}[!b]
				\begin{flalign}\label{eq:delta}
					\boldsymbol{\Delta}^\star
					&= \frac{1}{2} \beta_2 \rho (\boldsymbol{C}_{\mathrm{I},0}+\boldsymbol{C}_{\mathrm{P},0}) + \frac{3}{4} \beta_4 \rho^2
						\Biggl(
							2 t_{\mathrm{I},0}^{(i-1)} \boldsymbol{C}_{\mathrm{I},0} + \sum_{k=-N+1}^{N-1} (t_{\mathrm{P},k}^{(i-1)})^* \boldsymbol{C}_{\mathrm{P},k} + (t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)}) (\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0})&&\nonumber\\
					&\quad- (\boldsymbol{C}_{\mathrm{I},0} - \boldsymbol{C}_{\mathrm{P},0}) \mathrm{tr}\Bigl(
								(\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0}) \boldsymbol{\Phi}^\star
							\Bigr)
						\Biggr) + \mu^\star \sum_{n=1}^N \frac{(1-\rho) \boldsymbol{C}_n}{\sigma_n^2} \prod_{n'=1,n' \ne n}^N \Biggl(
						1 + \frac{(1-\rho)\mathrm{tr}\Bigl(
							\boldsymbol{C}_{n'} \boldsymbol{\Phi}^\star
						\Bigr)}{\sigma_{n'}^2}
					\Biggr) - \mathrm{diag}(\boldsymbol{\nu^\star}).&&
				\end{flalign}
			\end{figure*}
			Note that \eqref{eq:complementary_slackness} suggests $\mathrm{rank}(\boldsymbol{\Upsilon}^\star)+\mathrm{rank}(\boldsymbol{\Phi}^\star) \le L+1$. By reusing the proof in Appendix A of \cite{Xu2020}, we conclude $\mathrm{rank}(\boldsymbol{\Upsilon}^\star) \ge L$. On the other hand, $\boldsymbol{\Phi}^\star$ cannot be zero matrix and $\mathrm{rank}(\boldsymbol{\Phi}^\star) \ge 1$. Therefore, any optimal solution $\boldsymbol{\Phi}^\star$ to the relaxed problem~\eqref{op:irs_equivalent} is rank-\num{1}. Due to the equivalence between \eqref{ob:irs} and \eqref{ob:irs_equivalent}, $\boldsymbol{\Phi}^\star$ is also optimal to the relaxed problem~\eqref{op:irs} and Proposition~\ref{pr:relaxation} holds.
		\end{subsection}

>>>>

\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{array}
% \usepackage{caption}
\usepackage{cite}
\usepackage{colortbl}
\usepackage{environ}
\usepackage{grffile}
\usepackage{hyperref}
\usepackage{import}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{siunitx}
\usepackage{stfloats}
\usepackage{tikz}
\usepackage{url}
\usepackage{xcolor}
\usepackage[RPvoltages]{circuitikz}
\usepackage[T1]{fontenc}
\usepackage[caption=false,font=footnotesize]{subfig}
% \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
% \usepackage[cmintegrals]{newtxmath}
\usepackage[short]{optidef}
\usepackage[subtle]{savetrees}

@@

			\emph{Notations:} Scalars, vectors and matrices are denoted respectively by italic, bold lower-case, and bold upper-case letters. $j$ denotes the imaginary unit. $\boldsymbol{0}$ and $\boldsymbol{1}$ denote respectively zero and one vector or matrix. $\boldsymbol{I}$ denotes the identity matrix. $\mathbb{R}^{x \times y}$ and $\mathbb{C}^{x \times y}$ denote respectively the subspace spanned by real and complex $x \times y$ matrices. $\Re\{\cdot\}$ retrieves the real part of a complex entity. $(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $(\cdot)^+$, $\lvert{\cdot}\rvert$, $\lVert{\cdot}\rVert$ represent respectively the conjugate, transpose, conjugate transpose, ramp function, absolute value, and Euclidean norm. $\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{tr}(\cdot)$, $\mathrm{diag}(\cdot)$ and $\mathrm{diag}^{-1}(\cdot)$ denote respectively the argument, rank, trace, a square matrix with input vector on the main diagonal, and a vector retrieving the main diagonal of the input matrix. $\boldsymbol{S} \succeq \boldsymbol{0}$ means $\boldsymbol{S}$ is positive semi-definite. $\mathbb{A}\{\cdot\}$ extracts the DC component of a signal. $\mathbb{E}_X\{\cdot\}$ takes expectation w.r.t. random variable $X$ ($X$ is omitted for simplicity). The distribution of a CSCG random vector with mean $\boldsymbol{0}$ and covariance $\boldsymbol{\Sigma}$ is denoted by $\mathcal{CN}(\boldsymbol{0},\boldsymbol{\Sigma})$. $\sim$ means ``distributed as''. $(\cdot)^{(i)}$ and $(\cdot)^{\star}$ denote respectively the $i$-th iterate and the stationary solution.
		\end{subsection}
	\end{section}

@@

			Note that $t_{\mathrm{I/P},0}=\mathrm{tr}(\boldsymbol{C}_{\mathrm{I/P},0}\boldsymbol{\Phi})$ is real because $\boldsymbol{C}_{\mathrm{I/P},0}$ and $\boldsymbol{\Phi}$ are Hermitian matrices. Due to symmetry \cite{Huang2017}, we have
			\begin{equation}\label{eq:coupled_terms}
				\sum_{k=-N+1}^{N-1} \Re\left\{t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^*\right\} = \sum_{k=-N+1}^{N-1} t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^*.
			\end{equation}

@@

	\begin{section}{Performance Evaluations}\label{se:performance_evaluation}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{0.9\columnwidth}
			\import{assets/}{layout.pdf_tex}
			\caption{System layout in simulation.}
			\label{fi:layout}
		\end{figure}

		To evaluate the performance of the proposed IRS-aided SWIPT system, we consider the layout in Fig.~\ref{fi:layout} where the IRS moves along a line parallel to the AP-UE path. Let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the AP to the IRS, and denote respectively $d_{\mathrm{D}}$, $d_{\mathrm{I}}=\sqrt{d_{\mathrm{H}}^2+d_{\mathrm{V}}^2}$, $d_{\mathrm{R}}=\sqrt{(d_{\mathrm{D}}-d_{\mathrm{H}})^2+d_{\mathrm{V}}^2}$ as the distance of direct, incident and reflective links. Consider a large open space Wi-Fi-like environment at center frequency \SI{5.18}{\GHz}, where the fading parameters follow IEEE TGn channel model D \cite{Erceg2004} and the reference path loss is \SI{-35}{\dB} at \SI{1}{\meter}. Denote $\Lambda_{\mathrm{D}},\Lambda_{\mathrm{I}},\Lambda_{\mathrm{R}}$ as the path loss of direct, incident and reflective links. All channels are assumed NLoS with taps modelled as i.i.d. CSCG random variables of unit average sum-power, corresponding to a normalized multipath response. Rectenna parameters are chosen as $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\SI{50}{\ohm}$ such that $\beta_2=0.17$ and $\beta_4=957.25$. The average Effective Isotropic Radiated Power (EIRP) is fixed to $P=\SI{36}{\dBm}$ and the receive antenna gain is \SI{2}{\dBi}. Moreover, the scaling ratio is $\alpha=2$, the tolerance is $\epsilon=10^{-8}$, and we assume $\delta=\rho$ for simplicity. Each R-E region is averaged over \num{300} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.

@@

			We then derive the gradient explicitly and rewrite \eqref{eq:gradient} as
			\begin{equation}
				\boldsymbol{\Upsilon}^\star = \boldsymbol{I} - \boldsymbol{\Delta}^\star
			\end{equation}
			where $\boldsymbol{\Delta}^\star$ is given by \eqref{eq:delta}.
			\begin{figure*}[!b]
				\begin{flalign}\label{eq:delta}
					\boldsymbol{\Delta}^\star
					&= \frac{1}{2} \beta_2 \rho (\boldsymbol{C}_{\mathrm{I},0}+\boldsymbol{C}_{\mathrm{P},0}) + \frac{3}{4} \beta_4 \rho^2
						\Biggl(
							2 t_{\mathrm{I},0}^{(i-1)} \boldsymbol{C}_{\mathrm{I},0} + \sum_{k=-N+1}^{N-1} (t_{\mathrm{P},k}^{(i-1)})^* \boldsymbol{C}_{\mathrm{P},k} + (t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)}) (\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0})&&\nonumber\\
					&\quad- (\boldsymbol{C}_{\mathrm{I},0} - \boldsymbol{C}_{\mathrm{P},0}) \mathrm{tr}\Bigl(
								(\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0}) \boldsymbol{\Phi}^\star
							\Bigr)
						\Biggr) + \mu^\star \sum_{n=1}^N \frac{(1-\rho) \boldsymbol{C}_n}{\sigma_n^2} \prod_{n'=1,n' \ne n}^N \Biggl(
						1 + \frac{(1-\rho)\mathrm{tr}\Bigl(
							\boldsymbol{C}_{n'} \boldsymbol{\Phi}^\star
						\Bigr)}{\sigma_{n'}^2}
					\Biggr) - \mathrm{diag}(\boldsymbol{\nu^\star}).&&
				\end{flalign}
			\end{figure*}
			Note that \eqref{eq:complementary_slackness} suggests $\mathrm{rank}(\boldsymbol{\Upsilon}^\star)+\mathrm{rank}(\boldsymbol{\Phi}^\star) \le L+1$. By reusing the proof in Appendix A of \cite{Xu2020}, we conclude $\mathrm{rank}(\boldsymbol{\Upsilon}^\star) \ge L$. On the other hand, $\boldsymbol{\Phi}^\star$ cannot be zero matrix and $\mathrm{rank}(\boldsymbol{\Phi}^\star) \ge 1$. Therefore, any optimal solution $\boldsymbol{\Phi}^\star$ to the relaxed problem~\eqref{op:irs_equivalent} is rank-\num{1}. Due to the equivalence between \eqref{ob:irs} and \eqref{ob:irs_equivalent}, $\boldsymbol{\Phi}^\star$ is also optimal to the relaxed problem~\eqref{op:irs} and Proposition~\ref{pr:relaxation} holds.
		\end{subsection}
